### 2016-04-26 outline.tex
integrate notes into outline from two weeks ago
update outline with notes on translation of JMP model

\vskip.5in
\section{Median Legislator's Condition}
\begin{itemize}
	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
		\[
		  W\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W\left( \bta,\ga(e,\ta)\right)
		\]
		\begin{itemize}
			\item Need to make sure this is not always the case.
				\begin{itemize}
					\item Median legislator still has to balance (weighted) producers and consumers.
					\item If $\ga = 1$, would pick optimal tariff.
					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
				\end{itemize}
			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
			\item Need to check exec's SOC
		\end{itemize}
	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
\end{itemize}

@@

\vskip1in
Next steps:
\begin{enumerate}
	\item Check BS GE model
	\item Check on how results from JMP would translate given no punishments
	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$
\end{enumerate}

>>>>

\vskip.5in
\section{Median Legislator's Condition}
\begin{itemize}
	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
		\[
		  W\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W\left( \bta,\ga(e,\ta)\right)
		\]
		\begin{itemize}
			\item Need to make sure this is not always the case.
				\begin{itemize}
					\item Median legislator still has to balance (weighted) producers and consumers.
					\item If $\ga = 1$, would pick optimal tariff.
					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^N < \tau^{AD}$, depends on which is closer in welfare terms 
				\end{itemize}
			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
			\item Exec's SOC doesn't matter: going to take $\bta$ as given. But need to worry about lobby and leg SOCs. I've convinced myself that the relevant results from my JMP go through for this objective function, so SOCs go through too (given the right assumptions to get concavity for leg, or possibly the argumentation from trade war section supplied by RoIE editor)
		\end{itemize}
	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
		\begin{itemize}
			\item Could reduce form this, or not
		\end{itemize}
\end{itemize}

@@

\vskip.5in
Notes
\begin{enumerate}
	\item I don't think a more general model like BS1999 will work; I need to be able to pick apart the elements of the welfare function to separate out $\ga(e,\ta)$ in order to do my proofs
\end{enumerate}

\vskip1in
Next steps:
\begin{enumerate}
	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$
\end{enumerate}
